|

### 2022-11-08 manuscript.Rmd
better wording

Despite the increasing demand for accessibility knowledge in both industries and academia and the critical impact of accessible visualizations, accessibility has not yet found its place in the data science course and teaching materials. One main reason for this could be that accessibility is often incorporated into human-computer interaction (HCI) and design courses [@shinoharaHowDesigningPeople2016; @shinoharaTeachingAccessibilityTechnology2017a], introductory web development [@koAccessComputingPromotesTeaching2016; @rosmaitaAccessibilityFirstNew2006], software engineering courses [@martin-escalonaIntroductionTopicAccessibility2013; @ludiIntroducingAccessibilityRequirements2007; @ludiAccessEveryoneIntroducing2002] or the digital arts [@barata2019inclusion], if at all covered. However, data science is an interdisciplinary field that is taught in various disciplines, including not only computer and information sciences but also statistics, business schools, political science, biological sciences, and more [@schwab2021data]. Thus, we posit that the resources and conversations around accessibility have not yet extended to the broader data science education community at the scale that they should. For instance, many introductory data science courses [@yan2019first; @baumer2015data], textbooks [@adhikari2019computational; @wickham2016r], or curricula [@schwab2021data] either fail to mention accessibility at all or only focus on the accessing data.

@@

Some people may wonder why we need to teach accessibility as part of an introductory data science course as opposed to covering accessibility in a separate and general course module. According to the recent faculty survey on teaching accessibility [@shinoharaWhoTeachesAccessibility2018], the most critical barriers to teaching accessibility reported by 1,857 faculty from 318 institutions were "the absence of clear and *discipline-specific accessibility* [emphasis added] learning objectives and the lack of faculty knowledge about accessibility." <!-- Need to find the exact page number for this quote -->
This means faculty often have trouble making sense of how they can integrate accessibility into their specific teaching domains, which requires applied knowledge of accessibility beyond general concepts.

>>>>

Despite the increasing demand for accessibility knowledge in both industries and academia and the critical impact of accessible visualizations, accessibility has not yet found its place in the data science course and teaching materials. One main reason for this could be that accessibility is often incorporated into human-computer interaction (HCI) and design courses [@shinoharaHowDesigningPeople2016; @shinoharaTeachingAccessibilityTechnology2017a], introductory web development [@koAccessComputingPromotesTeaching2016; @rosmaitaAccessibilityFirstNew2006], software engineering courses [@martin-escalonaIntroductionTopicAccessibility2013; @ludiIntroducingAccessibilityRequirements2007; @ludiAccessEveryoneIntroducing2002] or the digital arts [@barata2019inclusion], if at all covered. However, data science is an interdisciplinary field that is taught in various disciplines, including not only computer and information sciences but also statistics, business schools, political science, biological sciences, and more [@schwab2021data]. Therefore, we posit that the resources and conversations around accessibility have not yet extended to the broader data science education community at the scale that they should. For instance, many introductory data science courses [@yan2019first; @baumer2015data], textbooks [@adhikari2019computational; @wickham2016r], or curricula [@schwab2021data] either fail to mention accessibility at all or only focus on the accessing data.

@@

Some people may wonder why we need to teach accessibility as part of an introductory data science course as opposed to covering accessibility in a separate and general course module. According to the recent faculty survey on teaching accessibility [@shinoharaWhoTeachesAccessibility2018], the most critical barriers to teaching accessibility reported by 1,857 faculty from 318 institutions were "the absence of clear and *discipline-specific accessibility* [emphasis added] learning objectives and the lack of faculty knowledge about accessibility." <!-- Need to find the exact page number for this quote -->
This reveals faculty often have trouble making sense of how they can integrate accessibility into their specific teaching domains, which requires applied knowledge of accessibility beyond general concepts.
